SNARL:\\Simulating Known Actors with Machine Learning

### 2017-05-15 tex/paper/paper.tex
Add bibliography.

\documentclass{amsart}
\usepackage{amsmath, amssymb, amsthm, hyperref, enumitem, multicol, caption, graphicx, float}

\usepackage[english]{babel}
\usepackage[autostyle, english=american]{csquotes}

@@

@@

\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

@@

\usepackage{fancyhdr}

\title{SNARL: Simulating Known Actors with Machine Learning}
\author{Bryan~Cai, Yasyf~Mohamedali\\ \MakeLowercase{bcai, yasyf}}

@@

\begin{titlepage}
\centering
~
\vspace{7 cm}
\maketitle
~\\
May 15, 2017
\vfill

\end{titlepage}

\section{Abstract}
We present SNARL, a suite of tools that is able to simulate a user's typing pattern with the goal of exposing the  vulnerabilities of new biometric based identification techniques. Researchers have known for many years that password based verifcation systems are insecure, in part due to security holes in applications, and in part due to users (eg password reuse). In an effort to bolster security, some applications leverage additional data; we are particularly interested in the merits and drawbacks of biometric data. Biometric identifications schemes are in some aspects very secure, because a person can often be uniquely identified by some combination of biometric factors. On the other hand, if somehow this information were to be stolen, akin to a password being leaked, it is nearly impossible to change, since they are often either physical traits that exist from birth or habits developed over many years. Our paper demonstrates a system that is able to rapidly learn and simulate user password typing habits, and suggests that keypress timings should only be used as an inexpensive technique that does not significantly boost security.

\begin{multicols*}{2}
\section{Introduction}

The past few years have seen several attempts to increase security in password-based authentication systems by adding secondary factors derived from biometric patterns in user behavior. Examples of this include Yang and Haddad's \texttt{punchTimeAuth} \footnote{http://css.csail.mit.edu/6.858/2017/projects/yangjy-ddh.pdf} and the commercial product being developed by UnifyID \footnote{https://unify.id}. However, there has not been much focus on the barrier this presents to attackers who are capable of mimicking their targets, particularly in the age of commodity cloud hardware and effective deep learning methods.

@@

All of the code for this paper can be found at \url{https://github.com/yasyf/skaml}.

@@

The first is a Google Docs look-alike \footnote{https://snarl.herokuapp.com}, which imitates a well-known service in a phishing-style attempt to convince a complacent user to type on the page. We overlayed a text box on a webpage containing the CSS from a Google Doc we created, allowing the user to type as if this were the application they are so familiar with. We implemented a small client-side library in JavaScript which listens for the \texttt{KeyDown} and \texttt{KeyUp} DOM events emitted from the textbox, so as to record the length of time each key is held for and the delay between key presses, as well as the actual characters being typed. This data is stored in a local buffer and is periodically uploaded to our servers, where a a Flask app records the logged objects to a MongoDB instance, tagged with a unique identifier for the user in question.

@@

The second technique we developed for data collection is a key-logging Google Chrome extension \footnote{https://snarl.herokuapp.com/client}. While the data quality from a document editor was vastly superior to the flow of data from casual bursts of typing in a browser, our models demanded as much data as we could possibly collect. Thus we augmented our corpus by creating an extension that injects a script into every web page, using the same library as before. We asked participants to install the extension and made them aware of the implications; our proof-of-concept was installed with consent but could just as easily be installed through less transparent means by a bad actor.

@@

The distinguisher model had a validation accuracy of 80\% to 85\%, which indicates that there is an appreciable difference between how distinct users type; however, it is clearly also not enought to uniquely identify a user. Again, this analysis suffers from low sample size, as we were only able to analyze 4 user's typing habits.

@@

\end{multicols*}

\begin{thebibliography}{99}

\bibitem{LSTM}  Zachary C. Lipton, David C. Kale, Charles Elkan, Randall Wetzell {\em Learning to Diagnose with LSTM Recurrent
Neural Networks}, arXiv:1511.03677, [2016].
\end{thebibliography}

@@

\grid

>>>>

\documentclass[9pt,journal]{IEEEtran}
\usepackage{graphicx,float,amsmath,amssymb,url,subcaption,array,fancyhdr}

\usepackage[english]{babel}
\usepackage[autostyle, english=american]{csquotes}
\usepackage[unicode]{hyperref}

@@

\usepackage[backend=biber]{biblatex}
\bibliography{paper}

@@

@@

\title{SNARL:\\Simulating Known Actors with Machine Learning}
\author{\IEEEauthorblockN{Bryan Cai, Yasyf Mohamedali}\\\IEEEauthorblockA{\{bcai, yasyf\}@mit.edu}}

@@

\maketitle

\section{Abstract}

We present SNARL, a suite of tools that is able to simulate a user's typing pattern with the goal of exposing the  vulnerabilities of new biometric based identification techniques. Researchers have known for many years that password based verifcation systems are insecure, in part due to security holes in applications, and in part due to users (eg password reuse). In an effort to bolster security, some applications leverage additional data; we are particularly interested in the merits and drawbacks of biometric data. Biometric identifications schemes are in some aspects very secure, because a person can often be uniquely identified by some combination of biometric factors. On the other hand, if somehow this information were to be stolen, akin to a password being leaked, it is nearly impossible to change, since they are often either physical traits that exist from birth or habits developed over many years. Our paper demonstrates a system that is able to rapidly learn and simulate user password typing habits, and suggests that keypress timings should only be used as an inexpensive technique that does not significantly boost security.

\section{Introduction}

The past few years have seen several attempts to increase security in password-based authentication systems by adding secondary factors derived from biometric patterns in user behavior. Examples of this include Yang and Haddad's \texttt{punchTimeAuth} \cite{punchtimeauth} and the commercial product being developed by UnifyID \cite{unifyid}. However, there has not been much focus on the barrier this presents to attackers who are capable of mimicking their targets, particularly in the age of commodity cloud hardware and effective deep learning methods.

@@

The code for the systems described in this paper can be found at \url{https://github.com/yasyf/snarl}.

@@

The first is a Google Docs look-alike \cite{gdocs}, which imitates a well-known service in a phishing-style attempt to convince a complacent user to type on the page. We overlayed a text box on a webpage containing the CSS from a Google Doc we created, allowing the user to type as if this were the application they are so familiar with. We implemented a small client-side library in JavaScript which listens for the \texttt{KeyDown} and \texttt{KeyUp} DOM events emitted from the textbox, so as to record the length of time each key is held for and the delay between key presses, as well as the actual characters being typed. This data is stored in a local buffer and is periodically uploaded to our servers, where a a Flask app records the logged objects to a MongoDB instance, tagged with a unique identifier for the user in question.

@@

The second technique we developed for data collection is a key-logging Google Chrome extension \cite{extension}. While the data quality from a document editor was vastly superior to the flow of data from casual bursts of typing in a browser, our models demanded as much data as we could possibly collect. Thus we augmented our corpus by creating an extension that injects a script into every web page, using the same library as before. We asked participants to install the extension and made them aware of the implications; our proof-of-concept was installed with consent but could just as easily be installed through less transparent means by a bad actor.

@@

The distinguisher model had a validation accuracy of 80\% to 85\%, which indicates that there is an appreciable difference between how distinct users type; however, it is clearly also not enought to uniquely identify a user. Again, this analysis suffers from low sample size, as we were only able to analyze four user's typing habits.

@@

\pagebreak
\printbibliography

@@
